Numerical analysis of the influence of magnetic field waveforms on the performance of active magnetic regenerators

### 2019-09-17 PaperMagneticProfiles_JBSMSE.tex
Add acknowledgements.
Compile manuscript to referee mode (bigger spacing and pictures).
Improve author's affiliations and addresses

% LaTeX .tex example for the proceedings of
% COBEM 2017 - 24th International Congress of Mechanical Engineering
% December, 3-8, 2017, Curitiba, PR, Brazil
%
% Based on the template of the proceedings of COBEM2015 
% MODELO COBEM 2017

\documentclass[draft]{svjour3}

@@

\institute{
Fábio P. Fortkamp 
\at
POLO --- Research Laboratories for Emerging Technologies in Cooling and Thermophysics, Department of Mechanical Engineering, Federal University of Santa Catarina, Florianópolis, SC, 88040-900, Brazil, \email{fabio@polo.ufsc.br}
\and
Gusttav B. Lang \and
Jaime A. Lozano \and
Jader R. Barbosa Jr. \at POLO --- Research Laboratories for Emerging Technologies in Cooling and Thermophysics, Department of Mechanical Engineering, Federal University of Santa Catarina, Florianópolis, SC, 88040-900, Brazil}

@@

\begin{acknowledgements}
This work was supported by CNPq, Embraco and EMBRAPII Unit Polo/UFSC.  
\end{acknowledgements}

>>>>

\documentclass[referee]{svjour3}

@@

\institute{
Fábio P. Fortkamp \\
\email{fabio@polo.ufsc.br} \\
Gusttav B. Lang \and
Jaime A. Lozano \and
Jader R. Barbosa Jr.
\at
POLO --- Research Laboratories for Emerging Technologies in Cooling and Thermophysics, Department of Mechanical Engineering, Federal University of Santa Catarina, Florianópolis, SC, 88040-900, Brazil}

@@

\begin{acknowledgements}
The authors duly acknowledge the financial support from CNPq (Grant no. 443696/2014-4), Capes (PTI program, Process no. 88887.194773/2018-00), Embraco and the EMBRAPII Unit Polo/UFSC.
\end{acknowledgements}
